Fig1

### 2020-05-15 analysis/figure-1.Rmd
now with better suppl fig and large file tracked

DEGbldg <- allDEG %>% 
  filter(grepl("bldg", comparison),
         !grepl("m.|early|extend|prolong", comparison))  %>%
  mutate(comparison = factor(comparison, levels = comparisonlevelsbldg))

@@

```{r supplfig-1, fig.width=5, fig.height=5}
s1a <- makebargraphsuppl(DEGcontrol, "hypothalamus","DEGs w/ + LFC", 0, 5000) + 
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) + 
  labs(subtitle = "hypothalamus") 
s1c <- makebargraphsuppl(DEGcontrol, "pituitary","DEGs w/ + LFC", 0, 5000)  +  
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())    + 
  labs(subtitle = "pituitary") 
s1e <- makebargraphsuppl(DEGcontrol, "gonad","DEGs w/ + LFC", 0, 5000) +  
  theme(strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlevelscontrol) +
  labs(subtitle = "gonads")

@@

plot_grid(a, s1, ncol = 1, rel_heights = c(0.25,1))
```

>>>>

DEGbldg <- allDEG %>% 
  filter(grepl("bldg", comparison),
         !grepl("m.|early|extend|prolong", comparison))  %>%
  mutate(comparison = factor(comparison, levels = comparisonlevelsbldg))  %>%
  drop_na()

@@

```{r supplfig-1, fig.width=5, fig.height=5}

sa <- png::readPNG("../figures/images/fig_supplfig1.png")
sa <- ggdraw() +  draw_image(sa, scale = 1)

s1a <- makebargraphsuppl(DEGcontrol, "hypothalamus","DEGs w/ + LFC", 0, 5000) + 
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) + 
  labs(subtitle = "hypothalamus") 
s1c <- makebargraphsuppl(DEGcontrol, "pituitary","DEGs w/ + LFC", 0, 5000)  +  
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())    + 
  labs(subtitle = "pituitary") 
s1e <- makebargraphsuppl(DEGcontrol, "gonad","DEGs w/ + LFC", 0, 5000) +  
  theme(strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlevelscontrol) +
  labs(subtitle = "gonads")

@@

supplfig1 <- plot_grid(sa, s1, ncol = 1, rel_heights = c(0.75,2))
supplfig1

pdf(file="../figures/supplfig-1-1.pdf", width=5, height=5)
plot(supplfig1)
dev.off()
```
